Association between trauma severity models and opportunities for improvement:

### 2022-12-14 manuscript.Rmd

@@

This is a single-centre retrospective cohort study, using data from two registries at Karolinska University Hospital: the trauma registry and the trauma care quality database. The trauma care quality database is a subset of the trauma registry and contains data on trauma patients who were selected for M&M reviews. These two databases were linked and then analysed to estimate the association between the common trauma severity models TRISS, NORMIT and PS and OFI using logistic regression. The predictive performance of these models was evaluated using measures of discrimination and calibration.

@@

Karolinska University Hospital is located in Solna, Sweden. The trauma centre at Karolinska University Hospital is equivalent to a level 1 trauma centre according to American College of Surgeons standards [@nksstats] and it is the primary trauma centre for the region of Stockholm. Karolinska University Hospital also has agreements with several other regions to provide trauma care for patients with severe trauma and the trauma centre has thereby a catchment population of almost 3 million residents [@nksstats].

The trauma registry at Karolinska University Hospital is part of SweTrau, Sweden's national trauma registry, and follows SweTrau guidelines. All trauma patients meeting the SweTrau inclusion criteria are registered in the trauma registry by research nurses at the trauma centre. Data is collected from the patient's electronic medical records. The trauma registry contains data on patients from 2013 to 2021. <!-- Based on the dates I see in the Swetrau dataset -->

@@

R, a programming language for statistical computing, was used for data collection and analysis. Logistic regression was used to estimate association between the estimates of the trauma severity models and OFI and the effect size was given as the OR. The CI for the OR was computed using the Wald estimator. Receiver operator characteristic (ROC) curves were used to assess diagnostic performance. The area under the curve (AUC) was calculated to compare the models with one another. The Integrated Calibration Index (ICI) was used to measure calibration. Accuracy was plotted and is reported as the accuracy at a 0.5 cutoff. Confidence intervals were calculated with bootstrapping. Results were presented with a confidence interval of 95%. A p-value of <0.05 was considered significant.

>>>>

<!-- how do they compare -->

@@

This is a single-centre retrospective cohort study, using data from two registries at Karolinska University Hospital: the trauma registry and the trauma care quality database. The trauma care quality database is a subset of the trauma registry and contains data on trauma patients who were selected for M&M reviews. These two databases were linked and then analysed to estimate the association between the common trauma severity models TRISS and NORMIT and OFI using logistic regression. The predictive performance of these models was evaluated using measures of discrimination and calibration.

@@

<!-- Describe the setting, locations, and relevant dates, including
periods of recruitment, exposure, follow-up, and data collection -->

Karolinska University Hospital is located in Solna, Sweden. The trauma centre at Karolinska University Hospital is equivalent to a level 1 trauma centre according to American College of Surgeons standards [@nksstats] and it is the primary trauma centre for the region of Stockholm. Karolinska University Hospital also has agreements with several other regions to provide trauma care for patients with severe trauma and the trauma centre has thereby a catchment population of almost 3 million residents [@nksstats]. 
The trauma registry at Karolinska University Hospital is part of SweTrau, Sweden's national trauma registry, and thereby follows SweTrau guidelines. All trauma patients meeting the SweTrau inclusion criteria are registered in the trauma registry by research nurses at the trauma centre. Data is collected from the patient's electronic medical records. The trauma registry contains data on patients from 2013 to 2021. <!-- Based on the dates I see in the Swetrau dataset -->

@@

R, a programming language for statistical computing, was used for data collection and analysis. Logistic regression was used to estimate association between the estimates of the trauma severity models and OFI and the effect size was given as the OR. The CI for the OR was computed using the Wald estimator. Receiver operator characteristic (ROC) curves were used to assess diagnostic performance. The area under the curve (AUC) was calculated to compare the models with one another. The Integrated Calibration Index (ICI) was used to measure calibration. Accuracy was plotted and is reported as the highest value for accuracy in the plot together with the associated cutoff. Results werepresented with a confidence interval of 95%. A p-value of <0.05 was considered significant.
